Evaluating Class Imbalance

### 2019-04-02 Scripts/evaluating_imbalance_ratios.Rmd
edits to results scripts

allirplots <- ggplot(allirdata, aes(x = Resolution, y = IR,fill = CL)) + 
  geom_bar(position = "dodge", stat="identity") + 
  ylab("Imbalance Ratio") +
  xlab("Resolution") +
  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
  labs(fill="Cell Line")+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

>>>>

allirplots <- ggplot(allirdata, aes(x = Resolution, y = IR,fill = CL)) + 
  geom_bar(position = "dodge", stat="identity") + 
  ylab("Imbalance Ratio") +
  xlab("") +
  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
  labs(fill="Cell Line")+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

# Evaluating number of bins

```{r}
binslist10 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/binslist10.rds")
binslist10 <- length(binslist10)
binslist25 <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/binslist25.rds")
binslist25 <- length(binslist25)
binslist50 <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/binslist50.rds")
binslist50 <- length(binslist50)
binslist100 <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/binslist100.rds")
binslist100 <- length(binslist100)

binslist10k <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/binslist10.rds")
binslist10k <- length(binslist10k)
binslist25k <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/binslist25.rds")
binslist25k <- length(binslist25k)
binslist50k <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/binslist50.rds")
binslist50k <- length(binslist50k)
binslist100k <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/binslist100.rds")
binslist100k <- length(binslist100k)

Bins <- c(binslist10,binslist25,binslist50,binslist100,
          binslist10k,binslist25k,binslist50k,binslist100k)
CL <- c(rep("GM12878", 4), 
                  rep("K562", 4))
Resolution <- c(rep(c("10 kb", "25 kb", "50 kb", "100 kb"), 2))

allbinsdata <- cbind.data.frame(Bins, CL, Resolution)
allbinsdata$CL <- factor(allbinsdata$CL, levels=c("GM12878", "K562"))
allbinsdata$Resolution <- factor(allbinsdata$Resolution, c("10 kb", "25 kb", "50 kb", "100 kb"))

allbinsplots <- ggplot(allbinsdata, aes(x = Resolution, y = Bins,fill = CL)) + 
  geom_bar(position = "dodge", stat="identity") + 
  ylab("Total Number of Genomic Bins\n(in thousands of basepairs)") +
  xlab("") +
  #scale_fill_manual(name="Cell Line", values=c("red", "blue"))+
  scale_y_continuous(limits=c(0,3e+05),
                     breaks=c(0, 1e+05, 2e+05),
                     labels = c("0", "100", "200")) +
  labs(fill="Cell Line")+
  theme_bw() +
  #guides(fill=FALSE)+
  theme(axis.text.x = element_text(size=15,
                                   angle = 45,
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))
```

```{r}
figure <- ggarrange(allbinsplots, allirplots, ncol = 2, nrow = 1, common.legend = TRUE, legend = "top")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20))
```
